draft_yma

### 2021-12-14 draft_yma.Rmd
boxcox transformation

ols_plot_resid_qq(full_fit)
ols_plot_resid_fit(full_fit)
```

@@

ols_plot_resid_fit(trans_fit)
ols_plot_resid_qq(trans_fit)

@@

boxcox

```{r}
lambda = boxcox(cdi_model$crm_1000~1)
optlam = lambda$x[which.max(lambda$y)]
```

>>>>

olsrr::ols_plot_resid_qq(full_fit)
olsrr::ols_plot_resid_fit(full_fit)
```

@@

olsrr::ols_plot_resid_fit(trans_fit)
olsrr::ols_plot_resid_qq(trans_fit)

@@
